\chapter{Useful Phrases}
\needspace{20\baselineskip}

\section*{Quick Reference}
\addcontentsline{toc}{section}{Quick Reference}

\begin{paracol}{2}
\huge{\color{wordColor}{English}}\\
\Large

\eng{"...and he stood holding his hat and turned his wet face to the wind..."}\\

\eng{Yes. }\\

\eng{No. }\\

\eng{Please. }\\

\eng{Thank you. }\\

\eng{Thank you very much. }\\

\eng{That's all right/You're welcome }\\

\eng{I love you.}\\

\eng{Do you speak ... }\\

\eng{\hspace{2cm}\@title }\\

\eng{\hspace{2cm}English }\\

\eng{\hspace{2cm}French }\\

\eng{I don't speak \@title }\\

\eng{Where is the phrase in this book? }\\

\eng{Just a minute. I'll see if I can find it in this book. }\\

\eng{I understand. }\\

\eng{I don't understand }\\

\eng{Could you talk more slowly please? }\\

\eng{Do you understand me ?}\\

\eng{I am hungry}\\

\eng{I am thirsty}\\

\eng{Where is the bathroom ?}\\

\eng{Where is the toilet ?}\\

\switchcolumn
\huge{\@title}\\
\Large

{bo de yirch bu chag yurd bo tech chag ixga un ös ro}\\
\\

{blah blah blah}\\

{blah blah blah}\\

{blah blah blah}\\

{blah blah blah}\\

\end{paracol}

\section*{Greetings and Civilities}
\addcontentsline{toc}{section}{Greetings and Civilities}
\begin{paracol}{2}
\huge{\color{wordColor}{English}}\\
\Large

\eng{Hello}\\

\eng{Hello, I'm ...}\\

\eng{I come from ...}\\

\eng{I live in ...}\\

\eng{\hspace{2cm}America}\\

\eng{\hspace{2cm}France}\\

\eng{Goodbye}\\

\eng{Good morning}\\

\eng{Good afternoon}\\

\eng{Good evening}\\

\eng{Good night}\\

\switchcolumn
\huge{\@title}\\
\Large

{blah blah blah}\\

{blah blah blah}\\

\end{paracol}

\section*{Shopping and Food}
\addcontentsline{toc}{section}{Shopping and Food}
\begin{paracol}{2}
\huge{\color{wordColor}{English}}\\
\Large

\eng{Where is a ... restaurant?}\\

     \eng{\hspace{2cm}Chinese}\\

     \eng{\hspace{2cm}Japanese}\\

     \eng{\hspace{2cm}kosher}\\

     \eng{\hspace{2cm}halal}\\

     \eng{\hspace{2cm}American}\\

     \eng{\hspace{2cm}vegetarian}\\

\eng{I'd like ...}\\

     \eng{\hspace{2cm}beef}\\

     \eng{\hspace{2cm}pork}\\

     \eng{\hspace{2cm}lamb}\\

     \eng{\hspace{2cm}rabbit}\\

     \eng{\hspace{2cm}eggs}\\

     \eng{\hspace{2cm}mouse}\\

     \eng{\hspace{2cm}peas}\\

     \eng{\hspace{2cm}beans}\\

     \eng{\hspace{2cm}peanuts}\\

     \eng{\hspace{2cm}eggs}\\

     \eng{\hspace{2cm}cabbage}\\

     \eng{\hspace{2cm}broccoli}\\

     \eng{\hspace{2cm}cauliflower}\\

     \eng{\hspace{2cm}lettuce}\\

     \eng{\hspace{2cm}tomato}\\

     \eng{\hspace{2cm}salad}\\

     \eng{\hspace{2cm}pepper (black/white)}\\

     \eng{\hspace{2cm}pepper (green/red/bell/hot)}\\

     \eng{\hspace{2cm}bread}\\

     \eng{\hspace{2cm}eggplant}\\

     \eng{\hspace{2cm}orange}\\

     \eng{\hspace{2cm}lemon}\\

     \eng{\hspace{2cm}grapefruit}\\

     \eng{\hspace{2cm}lime}\\

     \eng{\hspace{2cm}grape}\\

\eng{What's the price of this?}\\

\eng{That costs 13 [\@title~ monetary units] }\\

\eng{Where should I pay?}\\

\eng{I'm looking for something less expensive}\\

\eng{I would like to buy ...}\\

\eng{Where is the nearest bank?}\\

\eng{I would like to exchange American dollars for [\@title~ monetary units]}\\

\eng{What is the exchange rate ?}\\

\eng{Can you give me that ?}\\

\eng{I'd like you to give me that. }\\

\eng{Give me that. }\\

\eng{I want to buy that.}\\

\eng{Please sell me that. }\\

\eng{How much does this cost ?}\\

\eng{How much do you want to sell this ?}\\

\eng{Who sells this ?}\\

\eng{It is too expensive.}\\

\eng{I offer ... (amount of money) for this.}\\

\eng{Please, I'd like you to lend this to me.}\\

\eng{How long can I borrow it ?}\\

\eng{I don't have enough money.}\\

\eng{Give me some more.}\\



\switchcolumn
\huge{\@title}\\
\Large

{blah blah blah}\\

{blah blah blah}\\

\end{paracol}

\section*{Getting Around}
\addcontentsline{toc}{section}{Getting Around}
\begin{paracol}{2}
\huge{\color{wordColor}{English}}\\
\Large

\eng{Where is...}\\

\eng{How do I get to...}\\

\eng{\hspace{2cm}the train station}\\

\eng{\hspace{2cm}the bus station}\\

\eng{\hspace{2cm}the airport}\\

\eng{\hspace{2cm}the post office}\\

\eng{\hspace{2cm}the library}\\

\eng{\hspace{2cm}a restaurant}\\

\eng{I'd like a ticket to ...}\\

\eng{One way or round trip?}\\

\eng{One way }\\

\eng{Round trip }\\

\eng{Do I have to change trains?}\\

\eng{What platform does the train leave from? }\\

\eng{When is the first bus to ...?}\\

\eng{\hspace{2cm}…the next bus…}\\

\eng{\hspace{2cm}…the last bus…}\\

\eng{Please let me off at the next stop. }\\

\switchcolumn 
\huge{\@title}\\
\Large

{blah blah blah}\\

{blah blah blah}\\

\end{paracol}

\section*{Weather and Small Talk}
\addcontentsline{toc}{section}{Weather and Small Talk}
\begin{paracol}{2}
\huge{\color{wordColor}{English}}\\
\Large

\eng{Is it hot enough for you?}\\

\eng{Is it cold enough for you?}\\

\eng{Is it wet enough for you?}\\

\eng{It looks like rain.}\\

\eng{We could use the rain.}\\

\eng{It's so hot today you could fry an egg on the pavement.}\\

\eng{At least it's a dry heat.}\\

\eng{Does it always rain this much?}\\

\eng{Does the sun ever shine here?}\\

\eng{It's warmer than yesterday.}\\

\eng{It's colder than yesterday.}\\

\eng{I am ...-years-old}\\

\eng{I was born in ... (date)}\\

\eng{I was born in ... (place)}\\

\eng{I am ... tall (speaking about your height, unit unspecified) }\\

\eng{I am ... meters tall}\\

\eng{Can you speak language ... ?}\\

\eng{I speak English.}\\

\eng{I can speak French.}\\

\eng{I would like to visit ...}\\

\eng{I work as ... }\\

\eng{My mother is called ...}\\

\eng{Alice is my mother. }\\

\eng{My favorite color is ...}\\

\eng{I prefer the blue one over the red one.}\\

\eng{What's happening ?}\\

\eng{I'm lost}\\

\eng{I practice sport}\\

\eng{When are you born ?}\\

\eng{Where do you live ?}\\

\eng{What are you doing ?}\\

\eng{Where do you work ?}\\

\eng{What is your father's name ?}\\

\eng{Have you already been to place ... ?}\\

\eng{How much do you earn ?}\\

\eng{Where are you going to ?}\\

\eng{Where do you come from ?}\\

\eng{Did you know that ... ?}\\

\eng{What do you want me to do ?}\\

\eng{Can you help me ?}\\

\eng{Do you find me pretty ?}\\

\eng{May I guy you a drink ?}\\

\eng{Do you live with someone ?}\\

\eng{Are you married ?}\\

\eng{Do you have (a) lover(s) ?}\\


\switchcolumn
\huge{\@title}\\
\Large

{blah blah blah}\\

{blah blah blah}\\

\end{paracol}

\section*{Times, Dates and Festivals}
\addcontentsline{toc}{section}{Times, Dates and Festivals}
\begin{paracol}{2}
\huge{\color{wordColor}{English}}\\
\Large

\eng{It's one o'clock}\\

\eng{It's two o'clock}\\

\eng{It's noon.}\\

\eng{It's midnight.}\\

\eng{It's one fifteen.}\\

\eng{It's one thirty.}\\

\eng{It's one forty-five.}\\

\eng{It's half-past one.}\\

\eng{It's quarter after one.}\\

\eng{It's quarter to one.}\\

\eng{It's morning.}\\

\eng{\hspace{2cm}afternoon }\\

\eng{\hspace{2cm}evening}\\

\eng{\hspace{2cm}night}\\

\eng{It's today.}\\

\eng{\hspace{2cm}tomorrow}\\

\eng{\hspace{2cm}this week}\\

\eng{\hspace{2cm}next week}\\

\eng{\hspace{2cm}last week}\\

\eng{\hspace{2cm}this month}\\

\eng{\hspace{2cm}next month}\\

\eng{\hspace{2cm}last month}\\

\eng{\hspace{2cm}this year}\\

\eng{\hspace{2cm}next year}\\

\eng{\hspace{2cm}last year}\\

\eng{January}\\

\eng{February}\\

\eng{March}\\

\eng{April}\\

\eng{May}\\

\eng{June}\\

\eng{July}\\

\eng{August}\\

\eng{September}\\

\eng{October}\\

\eng{November}\\

\eng{December}\\


\eng{Sunday}\\

\eng{Monday}\\

\eng{Tuesday}\\

\eng{Wednesday}\\

\eng{Thursday}\\

\eng{Friday}\\

\eng{Saturday}\\


\eng{Spring}\\

\eng{Summer}\\

\eng{Winter}\\

\eng{Fall}\\


\eng{New Year's Day}\\

\eng{Vernal Equinox}\\

\eng{Summer Solstice}\\

\eng{Autumnal Equinox}\\

\eng{Winter Solstice}\\

\eng{Mother's Day}\\

\eng{Father's Day}\\

\eng{Birthday}\\


\switchcolumn
\huge{\@title}\\
\Large

{blah blah blah}\\

{blah blah blah}\\

\end{paracol}

\section*{Health and Medicine}
\addcontentsline{toc}{section}{Health and Medicine}
\begin{paracol}{2}
\huge{\color{wordColor}{English}}\\
\Large

\eng{Where is a doctor?}\\

\eng{Where is a hospital?}\\

\eng{It hurts here}\\

\eng{My head is too hot.}\\

\eng{I am sick}\\

\eng{I have a stomach ache}\\

\eng{\hspace{2cm}food poisoning}\\

\eng{\hspace{2cm}a fever.}\\

\eng{\hspace{2cm}an infection.}\\

\eng{\hspace{2cm}a headache.}\\

\eng{I've caught a cold.}\\

\eng{\hspace{2cm}the flu.}\\

\eng{\hspace{2cm}pneumonia.}\\

\eng{\hspace{2cm}a virus.}\\


\eng{Where is a nearby pharmacy?}\\

\eng{Do I need doctor's permission to use this medicine?}\\

\eng{Take this three times a day for the next two weeks.}\\

\eng{I need a (an)...}\\

\eng{\hspace{2cm}aspirin}\\

\eng{\hspace{2cm}antibiotic}\\

\eng{\hspace{2cm}herbal remedy}\\

\eng{\hspace{2cm}antacid}\\

\eng{\hspace{2cm}laxative}\\

\eng{\hspace{2cm}vitamin A}\\

\eng{\hspace{2cm}vitamin B3}\\

\eng{\hspace{2cm}vitamin C}\\

\eng{\hspace{2cm}condom}\\

\eng{\hspace{2cm}prescription.}\\

\switchcolumn
\huge{\@title}\\
\Large

{blah blah blah}\\

{blah blah blah}\\

\end{paracol}
